MSTK: Mesh Toolkit, v 1.83

### 2012-08-20 docs/MSTK.tex
Fixed error in declaration of MSTK_InitFromGenDesc

\item[]{\bf {\em int} MESH\_InitFromGenDesc({\em Mesh\_ptr} mesh, {\em
      int} nv, {\em double} (*xyz)[3], {\em int} *nfv, {\em int}
    **fvids, {\em int} nr, {\em int} *nrv, {\em int} **rvids, {\em
      int} *nrf, {\em int} ***rfvtemplate):} Initialize a mesh from a
  minimal description of the mesh passed into the routine. In the
  routine, {\bf nv} is the number of vertices or nodes and {\bf xyz}
  is the array of node coordinates. If the mesh is a surface mesh,
  {\bf nf} is the number of mesh faces, {\bf nfv} gives the number of
  vertices for each face, {\bf fvids} gives the array indices of the
  face vertices in ccw manner (starting from 0, not 1). If the mesh is
  a solid mesh, {\bf nr} specifies the number of solid elements or
  regions. If the mesh has only standard element types (tets,
  pyramids, triangular prisms and hexes), then {\bf nrv} indicates the
  number of vertices of each region and {\bf rvids} gives the array
  indices of the region vertices. If, on the other hand, the mesh has
  polyhedral elements, regions have to be described in terms of faces
  which are in turn described in terms of vertices. Therefore, {\bf
    nrf} indicates the number of faces for each region and {\bf
    rfvtemplate} gives the array indices of the vertices for each face
  of the region.

>>>>

\item[]{\bf {\em int} MESH\_InitFromGenDesc({\em Mesh\_ptr} mesh, {\em
      int} nv, {\em double} (*xyz)[3], {\em int} nf, {\em int} *nfv, 
    {\em int} **fvids, {\em int} nr, {\em int} *nrv, {\em int}
    **rvids, {\em int} *nrf, {\em int} ***rfvtemplate):} Initialize a
  mesh from a
  minimal description of the mesh passed into the routine. In the
  routine, {\bf nv} is the number of vertices or nodes and {\bf xyz}
  is the array of node coordinates. If the mesh is a surface mesh,
  {\bf nf} is the number of mesh faces, {\bf nfv} gives the number of
  vertices for each face, {\bf fvids} gives the array indices of the
  face vertices in ccw manner (starting from 0, not 1). If the mesh is
  a solid mesh, {\bf nr} specifies the number of solid elements or
  regions. If the mesh has only standard element types (tets,
  pyramids, triangular prisms and hexes), then {\bf nrv} indicates the
  number of vertices of each region and {\bf rvids} gives the array
  indices of the region vertices. If, on the other hand, the mesh has
  polyhedral elements, regions have to be described in terms of faces
  which are in turn described in terms of vertices. Therefore, {\bf
    nrf} indicates the number of faces for each region and {\bf
    rfvtemplate} gives the array indices of the vertices for each face
  of the region.
